Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-01-08 latex/figure3.tex
Change color for code background
Update syntax highlighting

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{import}\NormalTok{ numpy }\ImportTok{as}\NormalTok{ np}
\ImportTok{from}\NormalTok{ poincare }\ImportTok{import}\NormalTok{ Simulator}

\NormalTok{sim }\OperatorTok{=}\NormalTok{ Simulator(Oscillator)}
\NormalTok{df }\OperatorTok{=}\NormalTok{ sim.solve(save\_at}\OperatorTok{=}\NormalTok{np.linspace(}\DecValTok{0}\NormalTok{, }\DecValTok{5}\NormalTok{, }\DecValTok{101}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\end{minipage}%
\newline
\begin{minipage}[t]{0.50\linewidth}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df.head()}
\end{Highlighting}
\end{Shaded}

@@

\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{df.plot()}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{import} \ClassTok{numpy} \KeywordTok{as} \ClassTok{np}
\KeywordTok{from} \ClassTok{poincare} \KeywordTok{import} \ClassTok{Simulator}

\VariableTok{sim} \OperatorTok{=} \ClassTok{Simulator}\KeywordTok{(\ClassTok{Oscillator})}
\VariableTok{df} \OperatorTok{=} \VariableTok{sim}.\FunctionTok{solve}\KeywordTok{(}\VariableTok{save\_at}\OperatorTok{=}\ClassTok{np}.\FunctionTok{linspace}(\ValueTok{0}, \ValueTok{5}, \ValueTok{101})\KeywordTok{)}
\end{Highlighting}
\end{Shaded}

@@

\end{minipage}%
\newline
\begin{minipage}[t]{0.45\linewidth}

@@

\begin{Shaded}
\begin{Highlighting}[]
\VariableTok{df}.\FunctionTok{head}\KeywordTok{()}
\end{Highlighting}
\end{Shaded}

@@

\end{minipage}%
\hfill
\begin{minipage}[t]{0.45\linewidth}

@@

\begin{Shaded}
\begin{Highlighting}[]
\VariableTok{df}.\FunctionTok{plot}\KeywordTok{()}\OperatorTok{;}
\end{Highlighting}
\end{Shaded}

### 2024-01-08 latex/figure5.tex
Fix table format
Update syntax highlighting

\begin{Shaded}
\begin{Highlighting}[]
\ImportTok{from}\NormalTok{ simbio.io }\ImportTok{import}\NormalTok{ biomodels, sbml}

\NormalTok{model }\OperatorTok{=}\NormalTok{ sbml.load(}\StringTok{"repressilator.sbml"}\NormalTok{)  }\CommentTok{\# from existing SBML file}
\NormalTok{model }\OperatorTok{=}\NormalTok{ biomodels.load\_model(}\StringTok{"BIOMD12"}\NormalTok{)  }\CommentTok{\# from BioModels}
\NormalTok{model}
\end{Highlighting}
\end{Shaded}

\begin{longtable}{@{}lll@{}}
    \toprule\noalign{}
    Elowitz2000 - Repressilator \\
    type & total & names \\
    \midrule\noalign{}
    \endhead
    \bottomrule\noalign{}
    \endlastfoot
    variables  &  6 & PX, PY, PZ, X, Y, Z \\
    parameters & 17 & cell, beta, alpha0, alpha, eff, n, KM, tau\_mRNA, tau\_prot, ... \\
    equations  & 12 & Reaction1, Reaction2, Reaction3, Reaction4, Reaction5, ... \\
\end{longtable}

>>>>

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{from}\ClassTok{ simbio.io }\KeywordTok{import}\ClassTok{ biomodels, sbml}

\VariableTok{model }\OperatorTok{=}\ClassTok{ sbml}.\FunctionTok{load}\KeywordTok{(}\StringTok{"repressilator.sbml"}\KeywordTok{)}  \CommentTok{\# from existing SBML file}
\VariableTok{model }\OperatorTok{=}\ClassTok{ biomodels}.\FunctionTok{load\_model}\KeywordTok{(}\StringTok{"BIOMD12"}\KeywordTok{)}  \CommentTok{\# from BioModels}
\VariableTok{model}
\end{Highlighting}
\end{Shaded}

\begin{longtable}{@{}lll@{}}
    \multicolumn{3}{l}{Elowitz2000 - Repressilator} \\
    \toprule\noalign{}
    type & total & names \\
    \midrule\noalign{}
    \endhead
    \bottomrule\noalign{}
    \endlastfoot
    variables  &  6 & PX, PY, PZ, X, Y, Z \\
    parameters & 17 & cell, beta, alpha0, alpha, eff, n, KM, tau\_mRNA, tau\_prot, ... \\
    equations  & 12 & Reaction1, Reaction2, Reaction3, Reaction4, Reaction5, ... \\
\end{longtable}
